\LaTeXe\ guide for the Journal of Functional Programming

### 2019-10-16 papers/jfp/8-engineering.tex
Expand S8.9

>>>>

File-watching build systems face new engineering challenges. Firstly, a running
task may become \emph{obsolete} due to a concurrent modification of its direct
or transitive dependencies. To minimise the amount of unnecessary work, a
scheduler can \emph{cancel} the obsolete task and restart it once its
dependencies are up-to-date. Note that topological
schedulers~(\S\ref{sec-topological}) cannot be easily adapted to support such
situations, since a new topological sort may be required when file dependencies
change. A further complication is that spurious dependency cycles may form
during a series of file modifications, and a file-watching build system
integrated with an IDE should be able to cope with such spurious cycles
gracefully instead of terminating with an error.
